---
title: "apmaroul_homework5"
author: "Lexi Maroulakis"
date: "4/20/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r tidyverse, ECHO=TRUE}
require(tidyverse)
require(dplyr)
```

# homework 5
## loops

1) Create a for loop iterating from 1 to 26 that prints the statement “* is the n-th letter of the alphabet.” in each iteration.

```{r loopcreation}
alphabet <- c("a","b","c","d","e","f","g","h","i","j","k","l","m","n","o","p","q","r","s","t","u","v","w","x","y","z")
numbers<- list(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23,24,25,26)

for (i in 1:26){
  print(paste0(alphabet[i], " is the ", numbers[i], " letter of the alphabet"))
}
```

2) Create a variable called ‘count’ and set it equal to one. Then create a while loop with the condition‘count < 40’. Inside the loop, increase count by  1. Next, check if count is divisible by 4 using the %% operator; if it is, use a next statement. Otherwise, print the value of count to the console.

```{r counting}
count<-1
while(count < 40){
  count= count + 1
  print(count)
}
if (count%%4) {
next
}

```


## vectorized functions

3. Use apply to obtain the 5-number summary of each column of the built-in mtcars dataset.

```{r apply summary}
apply(X = select(mtcars, mpg:carb), MARGIN = 2,
 FUN = summary, na.rm = TRUE)

```

4. Consider the built-in iris dataset. Use the tapply to find the mean and standard deviation for Sepal.Length variable for each Species. 

You’ll need to check the help for tapply. It is similar to apply and lapply. Also, use group_by and summarize to find these values (they should be the same).

```{r mean sd and tapply}
smean<- tapply(iris$Sepal.Length, iris$Species, mean)
smean
ssd <-tapply(iris$Sepal.Length, iris$Species, sd)
ssd
```

5. Use the split function as below to create three lists - one for each species.
irislist <- split(iris$Sepal.Length,iris$Species).

Use the lapply function to conduct one-sample t-tests on each of the 3 vectors in irislist.

```{r lapply sepal length}
ilist <- split(iris$Sepal.Length,iris$Species)
lapply(ilist, FUN=t.test, alternatice=c("greater"), mu=6)
```

6. Create a vector ‘test_vec’ of the numbers 100 to 150. Then apply the following rules using only ifelse statements:

• if the number is divisible by 15, replace it with “FizzBuzz” (Recall from earlier the %% function.)

• if not, check if the number is divisible by 5 and, if so, replace it with “Buzz”

• if neither of the above, check if the number is divisible by 2 and, if so, replace it with “Fizz”

• otherwise, return the number

```{r test vec}
test_vec<- 100:150
test_vec = ifelse (test_vec%%15==0, "FizzBuzz", ifelse(test_vec%%5==0, "Buzz", ifelse (test_vec%%2==0, "Fizz", test_vec)))
```


## function writing

7. Create a function called convert_cm_to_in that converts centimeters to inches. Use your funciton to determine how many inches a 25cm object is.Next, evaluate your function at a vector of integers from 0 to 100 (1 meter).

```{r convert cm to in funct}
convert_cm_to_in <- function(x){
  vec=c()
  for(i in x){
    vec = append(vec, i/2.54)
  }
return(vec)
}
convert_cm_to_in(25)
hundred<- 0:100
convert_cm_to_in(hundred)

```

8. Add an addition input to the function that rounds the result to two decimal places by default. Rerun your function on the vector from 0 to 100.

```{r return funct 0 to 100}
Convert_cm_to_in= function(x, decimal =NULL){
  vec=c()
  for (i in x){
    vec=append(vec, i/2.54)
  }
  if(is.null(decimal))
    decimal = 2
  return (round(vec,decimal))
}
```

9. Create a function called count_my_change that adds up the total amount of money you input.

• Include 5 arguments - dollars, quarters, dimes, nickels, and pennies

• Set the default value of ALL the arguments to 0

• Calculate a total value by multiplying each argument by its dollar value (i.e. 0.25quarters, 0.01 pennies,etc.)

• Create a string that says “Your total is $amount” with the total, and put it inside a return statement to send it back to the user.

Try out the function with no inputs. Then try it with 5 dollars, 2 dimes, 3 quarters, 4 pennies, and 1 nickel.

```{r count my change}
count_my_change<-function(dollar=0, quarter=0, dime=0, nickel=0,penny=0){
  total= dollar+quarter*.25 +dime*.1 +nickel*.05 +peny*.01
  return(paste0("Your total is $", total))
}
```
